Exacerbated by the Pandemic: Analyzing the Impact of COVID-19 on Mortality Among Toronto's Homeless by Gender Disparities

### 2024-03-17 paper/paper.qmd
paper.qmd

The analysis will be conducted in [@citeR] and will utilize an array of packages such as [@citetidyverse], [@citereadr], [@citedplyr], and [@citeopendatatoronto] for data manipulation and analysis. All visualizations in this report are generated through [@citeggplot2], with tables crafted using [@citekableExtra].

>>>>

The analysis will be conducted in R [@citeR] and will utilize an array of packages such as tidyverse [@citetidyverse], readr [@citereadr], dplyr [@citedplyr], and opendatatoronto [@citeopendatatoronto] for data manipulation and analysis. All visualizations in this report are generated through ggplot2 [@citeggplot2], with tables crafted using kableExtra [@citekableExtra].For importing and exporting 'SPSS', 'Stata', and 'SAS' files, the haven package [@haven] will be used, alongside knitr [@citeknitr] for dynamic report generation in R.
